% === VI. CONCLUSION ===
\section{Conclusion}
\label{sec:conclusion}

This work has presented \system{}, a multimodal AI rehabilitation support system for elderly users. The system integrates real-time whole-body 3D pose estimation via RTMW3D-L (133 keypoints covering the body, hands, and face), multi-indicator facial state detection with OpenFace~3.0, voice-interactive LLM coaching, and a clinically-inspired six-dimensional scoring framework.

The main contributions are as follows. First, the system brings together, within a single real-time framework, whole-body 3D pose estimation, multi-indicator facial state detection, voice-interactive LLM coaching, and clinically-inspired kinematic scoring---capabilities that prior work has generally examined in isolation rather than as a unified pipeline. Second, a whole-body 3D pose estimation pipeline based on RTMW3D-L from MMPose delivers full 133-keypoint coverage and runs in real time on a single consumer GPU. Third, a multi-indicator facial state detection pipeline combines PSPI-inspired pain estimation, PERCLOS-based fatigue monitoring, blink and yawn detection, and engagement analysis. Finally, a DTW-based scoring framework evaluated on two public rehabilitation benchmarks yields a statistically significant, moderate correlation with clinical scores on KIMORE (Spearman $\rho = 0.347$, $p < 10^{-11}$) and strong exercise discriminability on UCO (AUC = 0.974, 48-point separation).

This paper is a feasibility study: the pipeline is computationally practical, and the scoring framework exhibits a statistically significant clinical signal, whereas clinical validation with elderly participants, ground-truth pose-accuracy benchmarking, and per-dimension weight calibration against clinician ratings remain future work.

Several directions are planned for future work. First, per-dimension scoring weights will be calibrated against physiotherapist assessments. Second, clinical user studies with elderly participants will be conducted to assess usability and therapeutic effectiveness. Third, metric-scale calibration will be explored to enable direct comparison with clinical goniometer measurements. Fourth, edge-based LLM deployment will be investigated to remove internet-connectivity requirements. Finally, multi-camera fusion will be pursued to address self-occlusion limitations.
