% === II. RELATED WORK ===
\section{Related Work}
\label{sec:related}

\subsection{Computer Vision-Based Rehabilitation}
Automated rehabilitation systems have evolved from sensor-based to vision-based approaches. Commercial platforms such as Sword Health and Hinge Health use wearable sensors with clinical validation~\cite{ref_sword_health}, while academic systems like Pose Trainer~\cite{ref_pose_trainer} demonstrated the feasibility of webcam-based exercise correction. Recent work on AIGC-based fitness feedback~\cite{ref_aigc_fitness} integrated pose estimation with LLM-generated feedback, but focused on general fitness rather than clinical rehabilitation. Comprehensive surveys~\cite{ref_pose_rehab_review} document the trend of combining vision-based pose analysis with natural language feedback, though none specifically target elderly users with whole-body multimodal feedback.

\subsection{3D Pose Estimation for Rehabilitation}
Accurate joint angle measurement demands 3D pose estimation. MediaPipe BlazePose~\cite{ref_blazepose} is widely adopted for rehabilitation owing to its speed (300+ FPS), but produces non-metric z-coordinates with approximately 63~mm MPJPE on Human3.6M~\cite{ref_mediapipe_accuracy}. State-of-the-art methods such as MotionBERT~\cite{ref_motionbert}, MotionAGFormer~\cite{ref_motionagformer}, and MeTRAbs~\cite{ref_metrabs} achieve 35--39~mm MPJPE, representing a 40--50\% improvement. Recent work on whole-body pose estimation, particularly RTMW3D~\cite{ref_rtmw3d} from MMPose~\cite{ref_mmpose}, extends coverage to 133 keypoints covering body, hands, and face in real-time, enabling comprehensive monitoring of exercise form including hand placement and facial expressions.

\subsection{Pain and Emotion Detection}
Facial Action Unit (AU) detection forms the basis for pain estimation through the Prkachin-Solomon Pain Intensity (PSPI) index~\cite{ref_pspi}. Deep learning approaches including JAA-Net~\cite{ref_jaanet} and ME-GraphAU~\cite{ref_me_graphau} have improved AU detection accuracy on standard benchmarks. For emotion recognition, MobileNetV3-Large and ViT-based models achieve 87--93\% on RAF-DB~\cite{ref_rafdb}. However, elderly faces present unique challenges: reduced expressiveness, skin texture confusion with wrinkles, and medication-induced facial masking~\cite{ref_elderly_faces}, necessitating lightweight, interpretable approaches for real-time deployment.

Fatigue detection has been extensively studied in driving safety, with PERCLOS~\cite{ref_perclos} (percentage of eye closure) the most validated metric. The Eye Aspect Ratio (EAR)~\cite{ref_ear} provides a computationally efficient proxy for eye closure detection. Engagement detection using facial AU analysis has been proposed by Whitehill et al.~(2014)~\cite{ref_engagement} and D'Mello \& Graesser~(2010)~\cite{ref_boredom}.

\subsection{LLM-Based Healthcare Assistance}
Large Language Models have been explored for rehabilitation guidance~\cite{ref_rehab_chatbot}. RAG-grounded LLMs reduce hallucinations by anchoring responses in verified clinical literature~\cite{ref_rag}. Current systems, however, lack integration with real-time pose analysis and voice interaction, particularly for elderly users who benefit from auditory guidance~\cite{ref_llm_rehab}. The safety of LLM-based medical advice remains a concern~\cite{ref_llm_medical_safety}, necessitating robust guardrails and contraindication checking.

\subsection{Biomechanics Metrics for Rehabilitation}
Quantitative assessment of exercise quality relies on biomechanics metrics. Joint angle computation methods range from simple dot-product (sagittal plane only) to quaternion-based approaches that handle multi-plane rotations without gimbal lock~\cite{ref_quaternion_angles}. The International Society of Biomechanics (ISB) provides standardized joint coordinate systems~\cite{ref_isb} for clinical angle reporting. Movement smoothness metrics include jerk-based measures~\cite{ref_ldlj} and Spectral Arc Length (SPARC), which is duration-independent and clinically validated for stroke rehabilitation~\cite{ref_sparc}. Dynamic Time Warping (DTW) variants, including weighted and constrained DTW~\cite{ref_dtw,ref_dtw_rehab}, enable robust motion comparison across different execution speeds---essential for elderly users who exercise at varying tempos.
